### 2019-08-14 paper_06_milestone/1st/article.tex
Rewrite chapter exp

The regime of strongly stratified turbulence, in which $ F_h $ is small and $
{\mathcal{R}} $ is large, is highly relevant for applications in the
ocean\cite[]{RileyDeBruynKops2003, Lindborg2006}, but is notoriously difficult
to reproduce in experiments and simulations. In trying to reach the strongly
stratified regime experimentally by increasing the degree of stratification,
the buoyancy Reynolds number often becomes so low that turbulence is totally
surpressed. Observations made in this regime suggest that $ \Gamma $ is
generally very small. Ivey \& Imberger \cite{IveyImberger1991} plotted mixing
efficiency derived from different laboratory measurements
\cite{Stillinger1983, Itsweire1986, Rohr1988, Lienhard1990} against a turbulent Froude
number. In the limit of large Froude number, the $ F_h^{-2} $-dependence is
clearly visible in all plots. At Froude number of the order of unity the
measurements indicate that $ \Gamma \approx 0.2 $, while at lower Froude
numbers, $ \Gamma $, or the related Richardson flux coefficient [Osborn], is
rapidly dropping below unity. In all likelihood, such observations are
artefacts of the limitation which is present in all observational studies of
strongly stratified turbulence, namely the severe difficulty in reaching the
regime where $ F_h $ is small while $ {\mathcal{R}} $ still is above a certain
limit. In the present study, we make an effort to push the limits further and
measure the mixing coefficient in a parameter regime which previously has not
been reached in laboratory studies. In particular, we focus on the regime, $ 10
< \mathcal{R} < 200 $, with $ F_h $ being as small as possible.

>>>>

The regime of strongly stratified turbulence, in which $ F_h $ is small and $
{\mathcal{R}} $ is large, is highly relevant for applications in the
ocean\citep[]{RileyDeBruynKops2003, Lindborg2006}, but is notoriously difficult
to reproduce in experiments and simulations. In trying to reach the strongly
stratified regime experimentally by increasing the degree of stratification,
the buoyancy Reynolds number often becomes so low that turbulence is totally
surpressed. Observations made in this regime suggest that $ \Gamma $ is
generally very small. Ivey \& Imberger \cite{IveyImberger1991} plotted mixing
efficiency derived from different laboratory measurements
\cite{Stillinger1983, Itsweire1986, Rohr1988, Lienhard1990} against a turbulent Froude
number. In the limit of large Froude number, the $ F_h^{-2} $-dependence is
clearly visible in all plots. At Froude number of the order of unity the
measurements indicate that $ \Gamma \approx 0.2 $, while at lower Froude
numbers, $ \Gamma $, or the related Richardson flux coefficient [Osborn], is
rapidly dropping below unity. In all likelihood, such observations are
artefacts of the limitation which is present in all observational studies of
strongly stratified turbulence, namely the severe difficulty in reaching the
regime where $ F_h $ is small while $ {\mathcal{R}} $ still is above a certain
limit. In the present study, we make an effort to push the limits further and
measure the mixing coefficient in a parameter regime which previously has not
been reached in laboratory studies. In particular, we focus on the regime, $ 10
< \mathcal{R} < 200 $, with $ F_h $ being as small as possible.
